Timeliness of security updates for Android

### 2014-08-01 securityupdates.tex
Start some evaluation

>>>>

\section{Evaluation}
Our results rely on the accuracy and representativeness of two data sets, the DeviceAnalyzer data and the AndroidVulnerabilities.org data.

Comparing the API version data from DeviceAnalyzer (Figure~\ref{fig:da_api}) with the ground truth data from Google Play (Figure~\ref{fig:play_api}) using ??? we find that ???.
Since API version is a coarse grained measure of OS version this means that the OS version distribution in DeviceAnalyzer ??? representative.
This shows that our data is ??? useful for examining the behaviour across the whole of Android.
However to compare different manufacturers we need to take small subsets of this data and then compare them.
Since there is no ground truth data available we cannot check definitively
